Guarded Recursion in Agda via Sized Types

### 2019-01-14 code-oneclock-paper/latex/paper.tex
First version of section 6 (The Interpretation)
Some textual fixes in sections 2 and 3

\section{Presheaf Semantics}
\label{sec:presheaf_sem}
\subsection{Presheaves}
\label{sec:presheaves}
\input{Presheaves/Presheaves}

@@

\input{Presheaves/Terminal}

\input{Presheaves/Sum}

\input{Presheaves/Product}

\input{Presheaves/Exp}

@@

\section{Modelling Guarded Recursion}
Now we got the simple type formers and their terms.
The next step is add the type formers required for guarded recursion.
We start by defining clock quantification and later, and how to construct terms of those types.
In addition, we define the fixpoint combinator.
We end this section by giving a type former for guarded recursive types.

>>>>

\section{Presheaf Semantics}
Next we define categorical semantics for the syntax defined in \Cref{sec:syntax}.
To do so, we use a similar method as used by M{\o}gelberg \cite{Mogelberg14}.
The interpretation of types depend on the clock contexts.
If the clock context is empty, then types become sets.
If the clock context has one clock, then types are interpreted as objects in the topos of trees.

\label{sec:presheaf_sem}
\subsection{Presheaves}
\label{sec:presheaves}
\input{Presheaves/Presheaves}

@@

@@

\section{Modelling Guarded Recursion}
\label{sec:guarded}
Now we got the simple type formers and their terms.
The next step is add the type formers required for guarded recursion.
We start by defining clock quantification and later, and how to construct terms of those types.
In addition, we define the fixpoint combinator.
We end this section by giving a type former for guarded recursive types.
